---
title: '6'
author: "JF"
date: "2024-10-07"
output: html_document
---

```{r setup, include=FALSE}
load("/Users/jadenfix/Desktop/Graduate School Materials/Advanced Econometrics 1/apple.RData")
head(data)
```
reglbs = β0 + β1(regprc) + β2(age) + β3(ecoprc) + β4(hhsize) + β5(faminc) + ε 

Estimate the model above using ordinary least squares, what is your estimate of β1, the price effect
```{r}
n = nrow(data)
X = cbind(rep(1,n), data$regprc, data$age, data$ecoprc, data$hhsize, data$faminc)
Y = data$reglbs
b = solve(t(X) %*% X) %*% (t(X)%*% Y)
b
B1 = b[2,1]
B1
```

What is the r^2?
```{r}
yhat = X %*% b 
SSE = sum((Y - yhat)^2)
SST = sum((Y - mean(Y))^2)
R2 = 1 - (SSE/SST)
R2
```
What is the adjusted r^2?
```{r}
p = ncol(X) - 1 
adj_R2 = 1-(1-R2)*(n-1)/(n-p-1)
adj_R2
```
Is the coeff estimate of B3 the correct sign?
```{r}
B3 = b[4,1]
B3
```
Add a new variable to the model that is defined as regprc × age. The coefficient on this variable will be β6. Re-estimate your model with this additional variable. What is your estimate of this new parameter?
```{r}
data$interactive = (data$regprc * data$age)
Xplus = cbind(X, data$interactive)
bplus = solve(t(Xplus) %*% Xplus) %*% (t(Xplus) %*% Y)
bplus 
B6 = bplus[7,1]
B6
```
Consider the price effect now ∂reglbs / ∂regprc = β1+β6age. This says that how responsive buyers are to price depends on age. Consider a buyer with age = 88. If regprc increases by $1, what will be the change in reglbs?
```{r}
B1 = bplus[2,1]
priceeffect1 = (B1 + (B6 * 88))
priceeffect1
```
Using your estimates, who would you say is more sensitive to price, older buyers or younger buyers? How is this conclusion relate to the sign on β6? Explain.
```{r}
#Since B6 is negative that means older buyers are more sensitive to price increases
```
reglbs = β0 + β1(regprc) + β2(age) + β3(ecoprc) + β4(hhsize) + β5(faminc) + ε 
a.) `r B1`
b.) `r R2`
c.) `r adj_R2` 
d.) `r B3` is the correct sign, high price of subs lead to increased purchases
e.) `r B6`
f.) `r priceeffect1`
g.) Since `r B6` is positive that means older buyers are less sensitive to price increases 