---
title: "Assignment 9"
author: "JF"
date: "2024-11-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
load("/Users/jadenfix/Desktop/Graduate School Materials/Advanced Econometrics 1/cornwell.RData")
df <- data
variable.names(df)
df = df[!is.na(df$crmrte),]
df = df[!is.na(df$polpc),]
df = df[!is.na(df$density),]
df = df[!is.na(df$pctymle),]
print(head(df))
```
A.) I am using polic/capita, density and % young male x1, x2, and x3
ols1 <- lm(crmrte ~ polpc + density + pctymle, data = df)
B.)
```{r}
ols1 <- lm(crmrte ~ polpc + density, data = df)
B1 = (ols1$coefficients["polpc"])
summary(ols1)
print(B1)
```
A 1 unit increase in police per capita is = to a 1.4093786 increase in crime rate holding density constant 
c.) 
```{r}
vcov_ols1 <- vcov(ols1)
var_x1 <- vcov_ols1["polpc", "polpc"]
se_x1 <- sqrt(var_x1)
print(vcov_ols1)
print(var_x1)
print(se_x1)
```
Variance is 0.03317612
SE is 0.1821431
ols1 <- lm(crmrte ~ polpc + density, data = df)
Part D.)
```{r}
s2 <- sum(residuals(ols1)^2) / (nrow(df) - length(coef(ols1)))
regression1 <- lm(polpc~density, data=df)
r2 <- summary(regression1)$r.squared
SST <- sum((df$polpc - mean(df$polpc))^2)
var_x1_same <- s2 / ((1-r2)*SST)
se_x1_same <- sqrt(var_x1_same)
print(var_x1_same)
print(se_x1_same)
```
They are the same: both are: 0.03317612
E.)
```{r}
ols2 <- lm(crmrte ~ polpc + density + pctymle, data = df)
vcov_ols2 <- vcov(ols2)
var_x1_ols2 <- vcov_ols2["polpc", "polpc"]
se_x1_ols2 <- sqrt(var_x1_ols2)
print(vcov_ols2)
print(var_x1_ols2)
print(se_x1_ols2)
```
The SE and Variance are slightly lower
F.)
```{r}
s2_withx3 <- sum(residuals(ols2)^2) / (nrow(df) - length(coef(ols2)))
print(s2_withx3)
regression123 <- lm(polpc~density+pctymle, data=df)
r2_x1_with_x2_x3 <- summary(regression123)$r.squared
print(r2_x1_with_x2_x3)
#SST stays the same 
SST <- sum((df$polpc - mean(df$polpc))^2)
print(SST)
var_x1_withx3 <- s2_withx3 / ((1-r2_x1_with_x2_x3)*SST)
se_x1_withx3 <- sqrt(var_x1_withx3)
print(var_x1_withx3)
print(se_x1_withx3)
```
F explanation: 
Residual variance decreased, implying pctymle helps capture additional variability in crmrte
partial R^2 increased by a little which means more variability is explained 
SST didnt change 
Variance of B1 decreased so it made the estimate a bit more accurate, while also increasing partial R^2
This means it helps increase accuracy without increasing multicolinearity, which implies its beneficial to add to the regression 