---
title: 'AE1: Assignment 3'
author: "Jaden Fix"
date: "2024-09-30"
output: html_document
---

Let's load in our data and make sure it's clean

```{r}
load("/Users/jadenfix/Desktop/Graduate School Materials/Advanced Econometrics 1/airfare.RData")
cleanness = any(is.na(data))
nrows = nrow(data)
print(paste("Question 1: Number of Rows:",nrows))
print(paste("FALSE means no N/As:",cleanness))
```

There are `r nrows` rows

```{r}
library(dplyr)
options(scipen=99999)
```

To Estimate a and b with the data: fare = a + b(passen)

```{r}
b_passen = cov(data$fare,data$passen)/var(data$passen)
print(paste("Question 2: coefficient b:",b_passen))
a_passen = mean(data$fare) - b_passen*mean(data$passen)
print(paste("Question 2: coefficient a:",a_passen))

```

Question 2: The correct value of a is `r a_passen` and the correct value of b is `r b_passen`

So we have: fare = `r a_passen` + `r b_passen` \* passen

Question 3: Total sum of squares for our y variable?

We need to do: TSS = sum(yi-yhat)\^2

```{r}

prediction <- a_passen + b_passen * data$passen
TSS = sum((data$fare - mean(data$fare))^2)
print(paste("TSS:",TSS))
```

```{r}
data$fittedfare <- a_passen + b_passen * data$passen
mean_fitted <- mean(data$fittedfare)
```

Fitted Value mean is `r mean_fitted`

```{r}
data$residuals <- data$fare - data$fittedfare
mean_residuals <- mean(data$residuals)
```

Mean of prediction errors: `r mean_residuals`

```{r}
SSE <- sum((data$residuals)^2)
```

SSE = `r SSE`

```{r}
Rsquared <- 1-(SSE/TSS)
```

Fraction of Variance = R\^2 = `r Rsquared`

```{r}
print(paste( "a:",nrows))
print(paste( "ba:",a_passen))
print(paste( "bb:",b_passen))
print(paste( "c:",TSS))
print(paste( "d:",mean_fitted))
print(paste( "e:",mean_residuals))
print(paste( "f:",SSE))
print(paste( "g:",Rsquared))

```

a.) `r nrows`

b.) `r a_passen` & `r b_passen`

c.) `r TSS`

d.) `r mean_fitted`

e.) `r mean_residuals`

f.) `r SSE`

g.) `r Rsquared`
