---
title: "Exam1"
author: "JF"
date: "2024-10-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load & Clean
```{r}
load("/Users/jadenfix/Desktop/Graduate School Materials/Advanced Econometrics 1/cornwell.RData")
df <- data
variable.names(df)
df = df[!is.na(df$crmrte),]
#head(df)
```
A.) I used police per capita, year and density 
B.) 
```{r}
modelshort <- lm(crmrte ~ polpc + year, data=df)
summary(modelshort)
```

```{r}
print(modelshort$coefficients["polpc"])
```
The coefficient polpc is = to 1.224996, implying a 1 unit increase in police per capita is = to a 1.224996 unit increase in crime rate 

C.) 
```{r}
modellong <- lm(crmrte ~ polpc + year + density, data=df)
summary(modellong)
```
The coefficient of polpc is 1.4127843, implying a 1 unit increase in police per capita is = to a 1.4127843 increase in crime rate 
```{r}
difference = (modelshort$coefficients["polpc"]) - (modellong$coefficients["polpc"])
print(difference) 
```
This is the difference between the 2 ^

D.) 
```{r}
int1 <- lm(density ~ polpc + year, data = df)
summary(int1)
```

```{r}
differenceint <- int1$coefficients["polpc"]*modellong$coefficients["density"]
print(differenceint)
```
Above is the difference between the 2^ (consistent with the other one)